The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
update funding, unify NSF acknowledgments

W.~Bangerth, T.~Heister, R.~Gassm{\"o}ller, and J.~Zhang were partially
supported by the Computational Infrastructure
for Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-1550901 and The
University of California -- Davis.

W.~Bangerth was also partially supported by award OAC-1835673 as part of the Cyberinfrastructure for Sustained Scientific Innovation (CSSI)
program, DMS-1821210,
and EAR-1925595.

@@

T.~Heister and J.~Zhang were also partially supported by NSF OAC-2015848.

T.~Heister was also partially supported by the NSF awards
DMS-2028346, EAR-1925575, and by
Technical Data Analysis, Inc. through US Navy STTR Contract N68335-18-C-0011.

R.~Gassm{\"o}ller was also partially supported by the National Science
Foundation (NSF) award EAR-1925595.

@@

M.~Maier was partially supported by ARO MURI Award No. W911NF-14-0247 and
NSF Award DMS-1912847.

D.~Wells was supported by the National Science Foundation (NSF) through Grant
DMS-1344962.

>>>>

W.~Bangerth, T.~Heister, R.~Gassm{\"o}ller, and J.~Zhang were partially
supported by the Computational Infrastructure for Geodynamics initiative
(CIG), through the National Science Foundation (NSF) under Award
No.~EAR-1550901 and The University of California -- Davis.

W.~Bangerth was also partially supported by Award OAC-1835673 as part of
the Cyberinfrastructure for Sustained Scientific Innovation (CSSI) program,
DMS-1821210, and EAR-1925595.

@@

T.~Heister and J.~Zhang were also partially supported by NSF
Award OAC-2015848.

T.~Heister was also partially supported by the NSF Awards DMS-2028346,
EAR-1925575, and by Technical Data Analysis, Inc. through US Navy STTR
Contract N68335-18-C-0011.

R.~Gassm{\"o}ller was also partially supported by the NSF Award
EAR-1925595.

@@

M.~Maier was partially supported by NSF Awards DMS-1912847 and DMS-2045636.

D.~Wells was supported by NSF through Grant DMS-1344962.
